Benchmarking Python Deep Learning Frameworks\\ on Language Modeling

### 2016-12-13 paper/main.tex
wrote more of the paper

Traditionally, neural models are trained until their performance on a \textit{development} set stops improving. Therefore, a full epoch of training (where all the training data is used) is usually followed by a predictive pass through development data.
\section{Benchmarks}
\subsection{Time}
We timed various things.
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & & 35h 25' & \\
Train epoch & & &  \\
Test epoch & & & \\
Train batch & & &  \\
Test batch & & & \\
\end{tabular}

\section{Discussion}
\section{Conclusion}
\newpage
\bibliography{references}
\bibliographystyle{emnlp16}
\end{document}

>>>>

Traditionally, neural models are trained until their performance on a \textit{development} set stops improving. Therefore, a full epoch of training (where all the training data is used) is usually followed by a predictive pass through development data.
\section{Benchmarks}
\subsection{Time}
The first benchmark to look at is how long training takes. Table \ref{tab:timing} summarizes various breakdowns.
\begin{table}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & & 35h 25' & \\
Train epoch & & 6h57' &  \\
Test epoch & & 7'45'' & \\
Train batch & & 5'' &  \\
Test batch & & $<$1'' & \\
\end{tabular}
\caption{\label{tab:timing}Total runtime on various subtasks.}
\end{table}

\subsection{Cuda Profiler}
We used the CUDA Profiler Toolkit \cite{nvprof} to characterized our implementations, specifically on a simplified task of training on 1 batch.

We profile which methods take the most amount of time, and look into a variety of metrics.
\begin{itemize}
\item \verb!achieved_occupancy! - fraction of GPU warps used v.s. total number of warps
\item \verb!sm_efficiency! - how much of the runtime is spent performing actual computation
\item \verb!warp_execution_efficiency! - how efficient is execution within a warp; number of registers per thread is a limiting factor.
\item \verb!warp_nonpred_execution_efficiency! - how efficient is execution within a warp on non-predicated (i.e. non-branching) instructions.
\item \verb!dram_read_throughput! - read throughput
\item \verb!dram_write_throughput! - write throughput
\end{itemize}
\section{Discussion}
When looking to use neural network benchmarks, researchers might want to consider various aspects.
\subsection{Programmer Experience}
When adopting new software frameworks, it is important to consider the potential learning curve, as well as higher-level advantages of each framework.

\subsection{TensorFlow}
Pros: easy to use; good support for RNNs and language models; 
Cons: symbolic computation graph is hard to debug; seems slower than others; 
\section{Conclusion}
\section*{Acknowledgments}
We want to thank Emily Furst for helping us with GPU profiling, specifically understanding the CUDA Profiler documentation.
\newpage
\bibliography{references}
\bibliographystyle{emnlp16}
\end{document}
